Measuring Lattices

### 2023-03-28 MeasuringLattices_uv5016/MeasuringLattices.tex
updating mostly Polar

@@

	In working with a space in which there are 
	multiple symmetry-related occurrences of items of interest (atoms, molecules, or,
	in this case, unit cells), it is conventional to choose a fundamental
	region. ``A fundamental domain or fundamental region is a subset of the space which contains exactly one point from each of these orbits. It serves as a geometric realization for the abstract set of representatives of the orbits.'' \cite{enwiki:1028832752}. In a two-dimensional graph, it would often be chosen as the all-plus
	quadrant. In crystallography, it might be a unit cell, a
	particular asymmetric unit of a crystal, or even a molecule.

@@

		\SVI{}: \citeasnoun{Andrews2019b} 
			presented a simple and the fastest currently
			known representation of lattices as the six Selling 
			scalars obtained from the dot products of the unit cell axes in addition to the negative of their sum (a body diagonal). Labeling 
			the cell axes ${\textbf{a}, \textbf{b}, \textbf{c}}$ , and ${\textbf{d}}$ (${\textbf{d}} =$ $-{\textbf{a}}-\!{\textbf{b}}-\!{\textbf{c}}$), 
			The scalars are	\vdotv{\textbf{b}}{\textbf{c}},~ \vdotv{\textbf{a}}{\textbf{c}},~ \vdotv{\textbf{a}}{\textbf{b}},
			~ \vdotv{\textbf{a}}{\textbf{d}},~ \vdotv{\textbf{b}}{\textbf{d}},~ \vdotv{\textbf{c}}{\textbf{d}} where,
			{\it e.g.},
			\vdotv{\textbf{b}}{\textbf{c}} represents the dot product of the ${\textbf{b}}$  and ${\textbf{c}}$  axes. For the purpose of organizing these six quantities as a vector space in which one can compute simple Euclidean distances, we describe this set of scalars 
			as a vector, ${\textbf{s}}$, with components, $ {s}_1, {s}_2, {s}_3, {s}_4, {s}_5, {s}_6 $.\\
		 		{ A cell is Selling-reduced if all six components are negative or zero \cite{Delaunay1932}.  
			\item Reversing the  observation that a Buerger-reduced cell is a good stepping stone to a Selling-reduced cell \cite{Allmann1968},
			a Selling-reduced cell can be a very efficient stepping stone to a Buerger-reduced cell from which a Niggli-reduced cell can quickly be derived.
			\item {Selling showed that the all-obtuse (Selling parameters all-negative) case is unique.
			 Every \SVI{} vector with all scalars non-positive corresponds to a valid unit cell.}

>>>>

In the following discussion we will follow the common practice of viewing the circle as a two-dimensional object and the torus as a three-dimensional object.   Formally, as a manifold, a circle is one-dimensional and a torus is a two-dimensional.”

@@

	In working with a space in which there are 
	multiple symmetry-related occurrences of items of interest (atoms, molecules, or,
	in this case, unit cells), it is conventional to choose a fundamental
	region. ``Given a topological space and a group acting on it, the images of a single point under the group action form an orbit of the action. A fundamental domain or fundamental region is a subset of the space which contains exactly one point from each of these orbits.'' \cite{enwiki:1028832752}. In a two-dimensional graph, it would often be chosen as the all-plus
	quadrant. In crystallography, it might be a unit cell, a
	particular asymmetric unit of a crystal, or even a molecule.

@@

		\SVI{}: \citeasnoun{Andrews2019b} 
			presented a simple and the fastest currently
			known representation of lattices as the six Selling 
			scalars obtained from the dot products of the unit cell axes in addition to the negative of their sum (a body diagonal). Labeling 
			the cell axes ${\textbf{a}, \textbf{b}, \textbf{c}}$ , and ${\textbf{d}}$ (${\textbf{d}} =$ $-{\textbf{a}}-\!{\textbf{b}}-\!{\textbf{c}}$), 
			The scalars are	\vdotv{\textbf{b}}{\textbf{c}},~ \vdotv{\textbf{a}}{\textbf{c}},~ \vdotv{\textbf{a}}{\textbf{b}},
			~ \vdotv{\textbf{a}}{\textbf{d}},~ \vdotv{\textbf{b}}{\textbf{d}},~ \vdotv{\textbf{c}}{\textbf{d}} where,
			{\it e.g.},
			\vdotv{\textbf{b}}{\textbf{c}} represents the dot product of the ${\textbf{b}}$  and ${\textbf{c}}$  axes. For the purpose of organizing these six quantities as a vector space in which one can compute simple Euclidean distances, we describe this set of scalars 
			as a vector, ${\textbf{s}}$, with components, $ {s}_1, {s}_2, {s}_3, {s}_4, {s}_5, {s}_6 $.\\
		 		{ A cell is Selling-reduced if all six components are negative or zero \cite{Delaunay1932}.  
			\item Reversing the  observation that a Buerger-reduced cell is a good stepping stone to a Selling-reduced cell \cite{Allmann1968},
			a Selling-reduced cell can be a very efficient stepping stone to a Buerger-reduced cell from which a Niggli-reduced cell can quickly be derived.
			\item {Selling showed that the all-obtuse (Selling parameters all-negative) case is unique \cite{Selling1874}.
			 Every \SVI{} vector with all scalars non-positive corresponds to a valid unit cell.}
